Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-26 jessie-writeup/jessie-writeup.tex
Defining J-embedding in Jessie's writeup

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}

@@

\begin{notation}
We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
\end{notation}

\begin{notation}
\jessiet{TODO: REVISIT THIS.  See Notation 3}
  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
  Note that $\varphi(\R') \subseteq \R$.
  %\jessie{Technically, if labeled, we also want a bijection $\phi: \R' \to \varphi(\R)$ so that $\phi(\gamma) = \Gamma \cap \varphi(\R')$, where $\phi = \varphi$ restricted to the range of $\varphi$.  We would then say $\gamma \preceq \Gamma$ if $\phi(\gamma) = \Gamma \cap \varphi(\R)$...?}
\end{notation}

\begin{notation}
\jessie{Attempt 2 of the above}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if there exists an injection $\varphi: \R' \to \R$ so that for all $p \in\P$, we have $\varphi(\gamma(p)) \in \Gamma(p)$. 
%\jessie{The $\cap \varphi(\R')$ isn't necessary anymore, right...?}
\end{notation}

@@

\begin{conjecture}
Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
\end{conjecture}
\begin{proof}
Assume $\gamma \preceq \Gamma$.
Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$.

Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
Therefore, $\gamma \approx \zeta$.
Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.

Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
The other direction follows with the same logic, using $\phi^{-1}$.
\end{proof}

In this case, we say $\zeta$ is a relabeling of $\gamma$.

@@

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable 	a.e.}

	Construct $\R := \{ r \in \reals^d : \exists p \in \P \text{ so that } r \in \Gamma(p) \}$, which is union of the elements in the range of $\Gamma$.

	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
	Observe that $\R'$ is finite and nonempty.
	Defining the property $\gamma = \Gamma\cap \varphi(\R')$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
	Removing redundant reports resolves (a.) and (b.).
	As $\Gamma$ is elicitable, we can see that (c.) cannot happen without contradicting elicitability by ... \jessie{closure of subgradient sets on the score $G$?}

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

\begin{proof}
	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.

	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.

	First, fix a level set $\theta \in \Theta'$.
	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.

	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.

	The other direction of inclusion follows from the same logic.
	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.

	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\gamma = \Gamma\cap \varphi(\R')$.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{\varphi(r)}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

@@

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

@@

	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
\end{proof}

@@

\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
We want to show that $\Gamma$ embeds this property $\gamma$.
We know $\gamma$ is nondegenerate and finite by construction.

@@

Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.

@@

\item [$1 \implies 6$]
Since $\strip(\gamma) = \trim(\Gamma)$ by Conjecture~\ref{conj:prec-if-embeds} and $\gamma$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\item [$2 \implies 4$]
	We know there is a nonredundant, nondegenerate $\gamma \preceq \Gamma$ so that $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	Take $\gamma, \varphi$, and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}, and $\R :=\varphi(\R')$. \jessie{$\varphi$ as defined in Notation 2 introducing $\preceq$}
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' = \varphi(r) \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then the level set $\Gamma_{r'} = \jessie{\subseteq ?} \gamma_r$ has empty interior by construction of $\R'$.

@@

\begin{lemma}\label{lem:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{lemma}
\begin{proof}
	If the property $\Gamma$ is nonredundant, there is a bijection $\phi:\R \toto \P$ so that $\phi(r) = \Gamma_r$ and $\phi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \phi(r_i), \theta_j = \phi(r_j)$ so that $\theta_i \subseteq \theta_j$.

	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \phi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ 	
	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}

>>>>

\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\cl}[1]{\text{cl}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\ones}{\mathbbm{1}}
\newcommand{\aff}{\text{aff}}
\newcommand{\im}{\text{im}}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\card}{\textbf{card}}

@@

%\begin{notation}
%We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \mapsto \Gamma(p) \cap \R'$.  
%\end{notation}

%\begin{notation}
%\jessiet{TODO: REVISIT THIS.  See Notation 3}
%  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
%  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
%  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
%  Note that $\varphi(\R') \subseteq \R$.
%\end{notation}
\begin{notation}
%\jessie{Attempt 2 of the above}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if for all $p \in \P$, we observe $\gamma(p) \subseteq \Gamma(p)$.
\end{notation}

@@

Observe that for every set of properties $\gamma: \P \toto \R'$ and $\zeta: \P \toto \R$ such that $\gamma \approx \zeta$, there is a bijection $\phi:\R' \to \R$ so that $\phi(\gamma(p)) = \zeta(p)$ for all $p \in \P$.
We slightly abuse notation and, given the finite set $S$, write $\phi(S) := \{\phi(x) : x \in S \}$.
($\phi$ is real valued, but we might be taking $\phi$ on every element of a (finite?) set.)

\begin{definition}
	The elicitable property $\Gamma:\P\toto \R$ is a \emph{J-embedding} of $\gamma: \P \toto \R'$ if there exists a property $\zeta : \P \toto \R$ so that $\zeta \preceq \Gamma$ and $\gamma \approx \zeta$.
\end{definition}

%\begin{conjecture}
%Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
%For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
%\end{conjecture}
%\begin{proof}
%Assume $\gamma \preceq \Gamma$.
%Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
%Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$. 
%
%Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
%Therefore, $\gamma \approx \zeta$.
%Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
%%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.
%
%Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
%The other direction follows with the same logic, using $\phi^{-1}$.
%\end{proof}
%
%In this case, we say $\zeta$ is a relabeling of $\gamma$.

@@

Other notes before starting:
\begin{itemize}
%\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
%We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
%\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets}

%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
%	Observe that $\R'$ is finite and nonempty.
	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
	Removing redundant reports resolves (a.) and (b.).
	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
	\jessie{... to do}

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\bigcup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

\begin{proof}
	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
	If $\zeta \not \approx \gamma$, then $\card(\R') \neq \card(\R)$.
	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.

%	We just want to show $\trim(\Gamma)$ is unique because of Conjecture~\ref{conj:gam-prime-exists}.	
%	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
%	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.
%	
%	First, fix a level set $\theta \in \Theta'$.
%	There is some report $r'$ so that $r' \in \Gamma(p) \cap \R'$ for all $p \in \theta$ by nondegeneracy of $\Gamma'$.
%	Now, for contradiction, suppose $\Gamma'_{r'} \not\in \strip(\tilde \Gamma)$.
%	Therefore, there is \emph{not} a report $r \in \tilde \R$ so that $\Gamma'_{r'} = \tilde \Gamma_r$.
%%	Now, if $\tilde \Gamma(p) = \emptyset$ for some $p \in \theta$, then we contradict nondegeneracy of $\tilde \Gamma$.
%	
%	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
%%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
%	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
%	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.
%	
%	The other direction of inclusion follows from the same logic.
%	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.
%	
%	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
%	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ and $\R'$ constructed in Conjecture~\ref{conj:gam-prime-exists}.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{r}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

@@

\begin{proof}
	\jessie{Original def of embedding}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

@@

	Therefore, every level set of the property $\Gamma$ is a subset of a level set of $\gamma$.
	\jessie{End embedding}

	\jessie{Begin J-embedding}
	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
	We know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
	Therefore, for every $r \in \reals^d$, there is some $r' \in \reals^d$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'} \iff p \in \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$ as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
	\jessie{End J-embedding}
\end{proof}

@@

\item[$5 \implies 1$] 
\jessie{Begin proof using Raf's definition of embedding... skip below for J embedding}
Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
We want to show that $\Gamma$ embeds this property $\gamma$.
We know $\gamma$ is nondegenerate and finite by construction.

@@

Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.
\jessie{End proof using Raf's definition of embedding}

\jessie{Begin J-embedding}
By Conjecture~\ref{conj:gam-prime-exists}, there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
\jessie{End J-embedding}

@@

\item [$1 \implies 6$]
Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\item [$2 \implies 4$]
	We know there is a nonredundant, nondegenerate proeprty $\gamma : \P \toto \R$ so that $\gamma \preceq \Gamma$ and therefore $\strip(\gamma) = \trim(\Gamma) = \Theta$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We then want to show $\strip(\Gamma) = \strip(\gamma) \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_{r'}$ for $r' = \varphi(r) \in \reals^d$.
	If $r' \in \R$, then $\Gamma_{r'} \in \strip(\gamma)$.
	If $r' \not \in \R$, then there is a report $r \in \R$ so that the level set $\Gamma_{r'} \subseteq \gamma_r$ has empty interior by Conjecture~\ref{conj:lev-sets-subsets}.

@@

\begin{lemma}\label{lem:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{lemma}
\begin{proof}
	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.

	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ 	
	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
